\section{Project Resources}

This chapter holds the project resources.

\subsection{Personnel}

\begin{itemize}
  \item \textbf{Milla \textsc{Mäkinen}} <\href{mailto:milla.makinen@student.tut.fi}{milla.makinen@student.tut.fi}> \\
        \emph{Scrum Master}, programmer and totally an artist. Industrial engineer, programmer at heart. Some five years of game dev experience mainly in C++ and Javascript. Specializes in having no life.
  \item \textbf{Mengyang \textsc{Chen}} <\href{mailto:mengyang.chen@student.tut.fi}{mengyang.chen@student.tut.fi}> \\
        Coder familiar with Javascript and C++, interested in web programming and game programming.
  \item \textbf{Daniel \textsc{Berezvai}} <\href{mailto:daniel.berezvai@student.tut.fi}{daniel.berezvai@student.tut.fi}> \href{http://3ice.hu/}{http://3ice.hu/} \\
        Product Owner, game modder (Warcraft 3),
  \item \textbf{Alexandre \textsc{Kirszenberg}} <\href{mailto:alexandre.kirszenberg@student.tut.fi}{alexandre.kirszenberg@student.tut.fi}>
        Programmer with previous experience as a Frontend Software Engineer. Interested in Software Development.
\end{itemize}

\subsection{Process description}

\paragraph{} The goal of our project is to make an interesting game, and pass the  course get the credits. To measure the success of the project, we will see whether the stories are fulfilled at the end.

\paragraph{} Basically we are going to use Whatsapp for discussion with each other and allocate the works evenly to everyone in the team, and use email to inform some general information to everyone in the team.

\paragraph{} To ensure the success of the project, one will inform other team members when facing some really tough tasks, so coding nights or jams will be held to solve the task together.

\subsection{Tools and technology}

\paragraph{} The tools used in this project are listed in Table \ref{table:tools}. Most of them are not affected by versioning as everyone is automatically updated to the latest version. If version difference issues arise, the contact person will decide which version everyone in the team will use.

\begin{table}[h]
\scriptsize
\captionof{table}{Tools used in the project}
\label{table:tools}
\begin{tabularx}{\textwidth}{|l|X|l|l|}
\hline
\rowcolor{Gray} \textbf{Purpose} & \textbf{Tool} & \textbf{Contact Person} & \textbf{Version} \\
\hline
Documentation & \LaTeX~ \href{https://www.latex-project.org/}{https://www.latex-project.org/} & & – \\
\hline
\multirow{2}{*}{Communication } & WhatsApp \href{http://www.whatsapp.com}{http://www.whatsapp.com} & M.M. & – \\
                                \cline{2-4}
                                & Skype \href{http://www.skype.org}{http://www.skype.org} & M.C. & – \\
\hline
Version management & GitLab \href{http://rd.gitlab.tut.fi}{http://rd.gitlab.tut.fi} \newline Accessible through the course selection or \href{https://gitlab.rd.tut.fi//sweng-2017/g22---yet-another-group}{https://gitlab.rd.tut.fi//sweng-2017/g22---yet-another-group} & M.M & – \\
\hline
Agile Management & AgileFant \href{https://app.agilefant.com}{https://app.agilefant.com} & & – \\
\hline
\end{tabularx}
\end{table}
