\begin{titlepage}

\newcommand{\HRule}{\rule{\linewidth}{0.5mm}} % Defines a new command for the horizontal lines, change thickness here

\center % Center everything on the page

%----------------------------------------------------------------------------------------
%   HEADING SECTIONS
%----------------------------------------------------------------------------------------

\textsc{\Large Project Plan and Study Diary}\\[0.5cm]
{\large Version \vhCurrentVersion ~from \vhCurrentDate}\\[1cm]

%----------------------------------------------------------------------------------------
%   TITLE SECTION
%----------------------------------------------------------------------------------------

\HRule \\[0.4cm]
{ \huge \bfseries G22 – Yet Another Group}\\[0.2cm]
{ \large \bfseries Yet Another Game (YAG)}\\[0.2cm]
\HRule \\[1.5cm]

%----------------------------------------------------------------------------------------
%   AUTHOR SECTION
%----------------------------------------------------------------------------------------

\begin{minipage}{\textwidth}
\begin{flushleft} \small
\emph{TUT – Pervasive Computing – TIE-21106 Software Engineering Methodology} \\[0.5cm]
\emph{Distribution: Farshad Ahmadi, Tero Ahtee, Kari Syst{\"a}} \\[0.5cm]
\emph{Document status:} Draft \\[0.5cm]
\emph{Authors:}\\
Milla \textsc{Mäkinen} <\href{mailto:milla.makinen@student.tut.fi}{milla.makinen@student.tut.fi}> \\
Mengyang \textsc{Chen} <\href{mailto:mengyang.chen@student.tut.fi}{mengyang.chen@student.tut.fi}> \\
Daniel \textsc{Berezvai} <\href{mailto:daniel.berezvai@student.tut.fi}{daniel.berezvai@student.tut.fi}> \\
Alexandre \textsc{Kirszenberg} <\href{mailto:alexandre.kirszenberg@student.tut.fi}{alexandre.kirszenberg@student.tut.fi}>
\end{flushleft}
\end{minipage}

\vspace{1.5cm}

\begin{versionhistory}
  \vhEntry{1.0}{28.01.2014}{Marko L.}{Initial version}
  \vhEntry{1.1}{11.02.2014}{Marko L.}{Deleted finnish text}
  \vhEntry{1.2}{18.01.2017}{Tensu}{Sections 1.4.x, cosmetic tuning}
  \vhEntry{1.3}{26.1.2017}{Marko L.}{Final toucher}
  \vhEntry{1.4}{16.01.2017}{Kari S.}{Adaptation for 2017 needs}
  \vhEntry{1.5}{25.01.2017}{Daniel B.}{Initial Shared document.}
  \vhEntry{1.6}{29.01.2017}{Alex K.}{Expand on risks.}
  \vhEntry{1.7}{29.01.2017}{Chen}{Process description}
  \vhEntry{1.8}{29.01.2017}{Daniel B.}{Final touches, layout fix, merge}
  \vhEntry{1.9}{29.01.2017}{Milla M.}{Tools, technologies, fixes}
  \vhEntry{1.10}{14.02.2017}{Alex K.}{Sprint 1}
  \vhEntry{1.11}{14.02.2017}{Daniel B.}{Doubled the length of each paragraph in our sprint 1 review. Detail rich explanations, miscellaneous fixes, and spellcheck. Clever titles introduced (I remembered to update Table of Contents too!). New tool: LaTeX. (A. K.)}
  \vhEntry{1.12}{12.03.2017}{Alex K.}{LaTeX version.}
  \vhEntry{1.13}{12.03.2017}{Alex K.}{Sprint 2}
  \vhEntry{1.14}{12.03.2017}{Milla M.}{Sprint 2 learning reflections, modified personnel info}
  \vhEntry{1.15}{12.03.2017}{Daniel B.}{Add distribution (teachers names) to titlepage.tex, as authored in the docx version (from template)}
  \vhEntry{1.16}{01.04.2017}{Daniel B.}{More minor edits to snippets, resources, and titlepage.tex (I just joined the cool kid club with pdfLaTeX and TeX Live. Before this I was using just TeX source code.)}
  \vhEntry{1.165}{02.04.2017}{Milla M.}{Sprint 3: The forgotten version edition. Added Sprint 3 learnings, Definition of Done and Git workflow}
  \vhEntry{1.17}{02.04.2017}{Daniel B.}{Sprint 3: Table of contents fixed so it shows up, long titles shortened, fits on one page. Some sections reordered.}
  \vhEntry{1.18}{03.04.2017}{Daniel B.}{Burndown graphs finished, added, and documented. Update effort left by hand when changing effort spent.}
  \vhEntry{1.19}{30.04.2017}{Milla M.}{Added some learnings for sprint 4 as well as text about the focus and summarization of the things learned in the whole project.}
\end{versionhistory}

\vfill % Fill the rest of the page with whitespace

\end{titlepage}
